Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-08-20 longSC.tex
Ilya and constantan's comments

\begin{equation}
E\frac{\mathrm{d}^3N}{\mathrm{d}{p}^3} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
\label{Eq:Fourier}
\end{equation}

@@

\section{Data Analysis}
\label{sec:experiment}
%The data samples analyzed in this article were recorded by ALICE during the 2010 heavy-ion run at the LHC in $\PbPb$ collisions at a centre-of-mass energy $\snn=2.76$~TeV.
The data samples of $\PbPb$ collisions at the centre-of-mass energy $\snn=2.76$~TeV analyzed in this article were recorded by ALICE during the 2010 heavy-ion run of the LHC.
Detailed descriptions of the ALICE detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0A and V0C) which cover the pseudorapidity  ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were included in the analysis. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The track reconstruction efficiency and contamination
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases with transverse momenta from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
Reconstructed TPC tracks constrained to vertex are required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (i.e. tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.

@@

%The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved shortly in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium due to its finite size and short lifetime. To address such non-equilibrium many-body dynamics, the AMPT model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
The initial conditions in the AMPT are given by the spatial and momentum distributions of minijets and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
For the data comparisons three different configurations of the AMPT model have been used: the default one and string melting with and without hadronic rescattering. The input parameters used in all configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb, while the Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
In the default configuration, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}. In the string melting configuration, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which includes resonance decays.
The string melting configuration of the AMPT without hadronic rescattering was used to study the influence of the hadronic phase on the development of the anisotropic flow.
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was observed in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV. It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}. The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.

@@

The calculations for the two sets of parameters which describe the lower order harmonic correlations best are compared to the data in Fig.~\ref{fig:Figure_3}. 
As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for the ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV. This parameterization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
The model calculations in which the temperature of the phase transition is larger than for ``param1'' are ruled out by the previous measurements~\cite{ALICE:2016kpq}.
%As shown in Fig.~\ref{fig:Figure_3}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are well described for the more central collisions and deviate by a little more than one sigma for 40--50\% centrality, as shown in Fig.~\ref{fig:Figure_3}.
%For correlations between $v_5$ and $v_3$, the model calculations underestimate the data slightly in more peripheral collisions.
%providing further independent constraints for the models.
%The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
In the case of $v_4$ and $v_3$, the same models underestimate the anti-correlation in the data significantly in mid-central collisions and it fails similarly for the anti-correlation between $v_3$ and $v_2$.
%Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.

@@

The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations. The ${\chi}^2$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$. This illustrates that the SC observables together with the individual flow harmonics provide better constraints for the model parameters than each of them individually.
%This finding supports the idea that the SC observables can provide better constraints in the model calculations than the individual flow harmonics $v_n$.

%As discussed in \cite{ALICE:2016kpq}, the other $\eta/s(T)$ parameterizations in event-by-event EKRT+viscous hydrodynamics give worse descriptions for SC(4,2) and NSC(4,2) compared to ``param1''. 
Once the calculations with an average over the temperature evolution of the expanding medium (constant $\eta/s$ parameterization ($\eta/s = 0.20$, ``param0'')) is compared to the temperature dependent $\eta/s$ parameterization (``param1'', where $\eta/s$ is the lowest ($\eta/s = 0.12$) at the temperature around 150~MeV),  in case of $v_n$, the ${\chi}^2$ values with ``param0'' are smaller than those with ``param1'' but the opposite trend is observed for SC($m$,$n$). Furthermore we observe a clear separation of two parameterizations for SC(5,3) which is even larger than SC(4,2).
These observations support that with the SC observables one can constraint the temperature dependent $\eta/s(T)$, taking one step further from estimating the simple average quantity $\eta/s$.

>>>>

\begin{equation}
E\frac{\mathrm{d}^3N}{\mathrm{d^3}{p}} = \frac{1}{2\pi}\frac{\mathrm{d}^2N}{p_{\mathrm{T}}\mathrm{d}p_{\mathrm{T}}\mathrm{d}\eta} \Big\{1 + 2\sum_{n=1}^{\infty} v_n(p_{\mathrm{T}},\eta) \cos[n(\varphi - \Psi_n)]\Big\},
\label{Eq:Fourier}
\end{equation}

@@

\section{Data Analysis}
\label{sec:experiment}
%The data samples analyzed in this article were recorded by ALICE during the 2010 heavy-ion run at the LHC in $\PbPb$ collisions at a centre-of-mass energy $\snn=2.76$~TeV.
The data sample of $\PbPb$ collisions at the centre-of-mass energy $\snn=2.76$~TeV analyzed in this article was recorded by ALICE during the 2010 heavy-ion run of the LHC.
Detailed descriptions of the ALICE detector can be found
in~\cite{Aamodt:2008zz,Carminati:2004fp,Alessandro:2006yt}. The Time
Projection Chamber (TPC) was used to reconstruct charged particle
tracks and measure their momenta with full azimuthal coverage in the
pseudorapidity range $|\eta|<0.8$. Two scintillator
arrays (V0A and V0C) which cover the pseudorapidity  ranges $-3.7<\eta<-1.7$
and $2.8<\eta<5.1$ were used for triggering and the determination of
centrality~\cite{Aamodt:2010cz}. The trigger
conditions and the event selection criteria are identical to those
described in~\cite{Aamodt:2010pa, Aamodt:2010cz}.
Approximately $10^7$ minimum-bias $\PbPb$ events with
a reconstructed primary vertex within $\pm 10$ cm from the nominal
interaction point along the beam direction are selected. Only charged particles reconstructed in the TPC in $|\eta|<0.8$
and $0.2<p_{\rm T}<5$~GeV/$c$ were included in the analysis. The charged track quality cuts
described in~\cite{Aamodt:2010pa} were applied to minimize
contamination from secondary charged particles and fake tracks.
The track reconstruction efficiency and contamination
were estimated from HIJING Monte Carlo
simulations~\cite{Wang:1991hta} combined with a GEANT3~\cite{Brun:1994aa} detector model and were found to be independent of
the collision centrality. The reconstruction efficiency increases with transverse momenta from
70\% to 80\% for particles with $0.2<p_{\rm T}<1$~GeV/$c$ and remains
constant at $(80 \pm 5)$\% for $p_{\rm T}>1$~GeV/$c$. The estimated
contamination by secondary charged particles from weak decays and
photon conversions is less than 6\% at $p_{\rm T}=0.2$~GeV/$c$ and falls
below 1\% for $p_{\rm T}>1$~GeV/$c$.
The $p_{\rm T}$ cut-off of 0.2~GeV/$c$ reduces event-by-event biases due to small reconstruction efficiency 
at lower $p_{\rm T}$, while the high $p_{\rm T}$ cut-off of 5~GeV/$c$ reduces the effects of jets on the measured correlations. 
Reconstructed TPC tracks constrained to vertex are required to have at least 70 space points (out of a maximum of 159). 
Only tracks with a transverse distance of closest approach to the primary vertex less than 3 mm, both in the longitudinal and transverse directions, are accepted. This reduces the contamination from secondary tracks produced in the detector material, particles from weak decays, etc. Tracks with kinks (i.e. tracks that appear to change direction due to multiple scattering or $K^{\pm}$ decays) were rejected.

@@

%The centrality dependence of the SC observables is compared to that in the {AMPT} model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en}.
Even though thermalization could be achieved shortly in collisions of very large nuclei and/or at extremely high energy~\cite{Kurkela:2015qoa}, the dense matter created in heavy-ion collisions may not reach full thermal or chemical equilibrium due to its finite size and short lifetime. To address such non-equilibrium many-body dynamics, the AMPT model~\cite{Zhang:1999bd,Lin:2000cx,Lin:2004en} has been developed, which includes both initial partonic and final hadronic interactions and the transition between these two phases of matter.
The initial conditions in the AMPT are given by the spatial and momentum distributions of minijets and soft strings from the HIJING model~\cite{Wang:1991hta,Gyulassy:1994ew}.
For the data comparisons three different configurations of the AMPT model have been used: the default one and string melting with and without hadronic rescattering. The input parameters used in all configurations are: $\alpha_s = 0.33$, a partonic cross-section of 1.5~mb.
In the default configuration, partons are recombined with their parent strings when they stop interacting. The resulting strings are later converted into hadrons using the Lund string fragmentation model~\cite{Andersson:1986gw,NilssonAlmqvist:1986rx}.
The Lund string fragmentation parameters were set to $\alpha = 0.5$ and $b = 0.9$~GeV$^{-2}$.
In the string melting configuration, the initial strings are melted into partons whose interactions are described by the ZPC parton cascade model~\cite{Zhang:1997ej}. These partons are then combined into the final state hadrons via a quark coalescence model. 
In both configurations, the dynamics of the subsequent hadronic matter is described by a hadronic cascade based on A Relativistic Transport (ART) model~\cite{Li:2001xh} which includes resonance decays.
The string melting configuration of the AMPT without hadronic rescattering was used to study the influence of the hadronic phase on the development of the anisotropic flow.
Even though the string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably well reproduces particle yields, $p_{\rm T}$ spectra, and $v_2$ of low $p_{\rm T}$ pions and kaons in central and mid-central $\AuAu$ collisions at $\snn=200$~GeV and $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Lin:2014tya}, it was observed in a recent study~\cite{Adam:2016nfo} that it fails to quantitatively reproduce the flow harmonics of identified hadrons ($v_2$, $v_3$, $v_4$ and $v_5$) at $\snn=2.76$~TeV. It turns out that the radial flow in AMPT is 25\% lower than that measured at the LHC, which is responsible for this quantitative disagreement~\cite{Adam:2016nfo}. The details of the AMPT configurations used in this article and the comparisons of $p_{\rm T}$-differential $v_{n}$ for pions, kaons and protons to the data can be found in \cite{Adam:2016nfo}.

@@

The calculations for the two sets of parameters which describe the lower order harmonic correlations best are compared to the data in Fig.~\ref{fig:Figure_3}. 
As can be seen in Fig.~1 from Ref.~\cite{Niemi:2015qia}, for the ``param1'' parameterization the phase transition from the hadronic to the QGP phase occurs at the lowest temperature, around 150~MeV. This parameterization is also characterized by a moderate slope in $\eta/s(T)$ which decreases (increases) in the hadronic (QGP) phase.
The model calculations in which the temperature of the phase transition is larger than for ``param1'' are ruled out by the previous measurements~\cite{ALICE:2016kpq}.
%As shown in Fig.~\ref{fig:Figure_3}, the correlations between $v_5$ and $v_2$ are well described for all available centralities and similarly for the correlations between $v_5$ and $v_3$ within the errors.
While the correlations between $v_5$ and $v_2$ are well described at all centralities, the correlations between $v_5$ and $v_3$ are reproduced in 0--40\% centrality range and deviate by about one sigma for 40--50\% centrality.
%For correlations between $v_5$ and $v_3$, the model calculations underestimate the data slightly in more peripheral collisions.
%providing further independent constraints for the models.
%The model calculations for SC(5,2) and SC(5,3) give better description than the correlations between $v_4$ and $v_2$. 
In the case of $v_4$ and $v_3$, the same models underestimate the anti-correlation in the data significantly in mid-central collisions and it fails similarly for the anti-correlation between $v_3$ and $v_2$.
%Most notably, this measurement is so far the most dramatic example of the failure of constant $\eta/s$ to describe the data.

@@

The ${\chi}^2$ values for $v_2$ and $v_3$ are significantly smaller than those for SC(3,2) and NSC(3,2) for all the hydrodynamic calculations. The ${\chi}^2$ values for SC(4,2) and NSC(4,2) from event-by-event EKRT+viscous hydrodynamics are comparable to that for $v_2$ but larger than for $v_4$. The ${\chi}^2$ for calculations for $v_n$ with constant $\eta/s$ = 0.20 (``param0'') are smaller than those with temperature dependent $\eta/s$ parameterization with a minimal value of $\eta/s$ = 0.12 at the temperature around 150 MeV (``param1''), while an opposite trend is observed for SC($m$,$n$), in particular for SC(4,2) and SC(5,3). 
This illustrates that a combination of the SC($m$,$n$) observables with the individual flow harmonics $v_n$ may provide sensitivity to the temperature dependence of the $\eta/s(T)$ and together they allow for better constraints of the model parameters.

%This illustrates that the SC observables together with the individual flow harmonics provide better constraints for the model parameters than each of them individually.
%Once the calculations with an average over the temperature evolution of the expanding medium (constant $\eta/s$ parameterization ($\eta/s = 0.20$, ``param0'')) is compared to the temperature dependent $\eta/s$ parameterization (``param1'', where $\eta/s$ is the lowest ($\eta/s = 0.12$) at the temperature around 150~MeV),  in case of $v_n$, the ${\chi}^2$ values with ``param0'' are smaller than those with ``param1'' but the opposite trend is observed for SC($m$,$n$). Furthermore we observe a clear separation of two parameterizations for SC(5,3) which is even larger than SC(4,2).
%These observations support that with the SC observables one can constraint the temperature dependent $\eta/s(T)$, taking one step further from estimating the simple average quantity $\eta/s$.
